Resume \\ Maha Mohammed Nabeel El Meseery

### 2011-01-11 MyCv/Resyne.tex
after editing the CV

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{-0.25in}
\setlength\textheight{10.0in}
\setlength\textwidth{6.5in}
\setlength\oddsidemargin{-0.25in}
\setlength\evensidemargin{-0.25in}
\setlength\parindent{0in}
\setlength\parskip{0in}

@@

%%% remove comment delimiter ('%') and select language if required
%\selectlanguage{spanish}
\maketitle
\section*{Personal Information:}
\noindent
 \textbf{ Address: } 2nd Tahreer street, Dokki, Giza 12615, Egypt.

\textbf{  Email: } melmeseery@gmail.com, melmeseery@aucegypt.edu.
 \section*{Education:}
  \begin{description}
 \item [2004-2009]  \textbf{ Msc.E., Cairo University, Computer Engineering Department, Giza, Egypt}\\
 Thesis Area:\textbf{\textit{Sketch Recognition And Understanding}.}\\
 Thesis Supervisors: \textit{Prof. Nevin Darwish (Cairo University), Dr Magda
 Fayek (Cairo University), Prof. Samia Mashali (Electrical Research Institute),
 Mahmoud Fakr El Din (Electrical Research Institute).}
 \item[1998-2003]  \textbf{ Bsc.E., Cairo University, Computer Engineering Department Giza, Egypt}\\
  Final Grade: \textbf{Very Good with honors.}\\
  Graduation project: \textit{Personal Face identification System,} \textbf{Distinction.}\\
  Project Supervisors: \textit{Dr. Madga Fayek.}
\item [1995-1998]  \textbf{General Secondary School Certificate,   Manar
 Language School. }
  \end{description}

 \section*{Experience:}
 %\textbf{\underbar{Experience:}}
 \textbf{August 2008- present   [part time]}\\
 \textbf{Research and Teaching Assistant}, American University in Cairo, Electrical Engineering Department.
 The following is summary of my achievements:
 \begin{enumerate}
   \item Conducted and helped develop research in Online Arabic Handwriting Recognition. This includes implementing various features extraction and classification methods.
   \item Assisted in collecting, gathering and analyzing an Online Arabic handwriting Dataset.
   \item Assisted and developed research in area of Arabic and Latin digit Recognition.
 \item Implementing different features extraction and classification methods for Arabic and Latin digits and comparing their performance.
 \item Read, analyzed and reviewed scientific and research papers.
 \item Wrote and edited research paper in topics related to Arabic Handwriting Recognition.
 \item Guided students in their studies in Lab projects and programming assignments.
 \item Conducted Tutorials and problem sessions for students in various subjects.
\end{enumerate}

 \textbf{January 2007- present}\\
 \textbf{Research Assistant}, Electrical Research Institute, Egypt
 \begin{enumerate}
\item Worked as a member of the Signal Processing Lab in the Computer and Systems Department.
 \item Assisted in the research project undergoing in the department.
 \item Helped in writing research papers on various topics.
 \item Implemented and develop different algorithms in field of Image Processing.
 \item Provided a technical support for other researchers especially in field of JavaEE programming.
\end{enumerate}

 \textbf{September 2005- September 2008 [part time from January 2007] }\\
 \textbf{Senior Software Engineer}, EngNet Company\textbf{}
 The following is summary of my achievements:
 \begin{enumerate}

@@

 \textbf{September 2003- September 2005}\\
 \textbf{Teaching Assistant}, Faculty of Computer Science, MSA University, Giza, Egypt.\textbf{}
 \begin{enumerate}
\item Developing lab manuals and leading lab experiments for Software Engineering Methodologies, Object Oriented Programming, Digital Logic Design, Computer Graphics, Calculus, and Introduction to IT.
 \item Guide students in their studies in Data Structure and algorithm, Object Oriented Programming, Software Engineering, Digital Logic Design, Computer Graphics, and Calculus.
 \item Assist and supervise student's projects and assignments in subjects mentioned.
 \item Assistant supervisor for senior student's projects (Mainly graduation project using ASP.Net, C\#) .
 \item Developing and delivering short courses in C++, C\#, UML, and ASP.NET.
\end{enumerate}

 \section*{Publications}
 \begin{enumerate}
  \item Online Library of Scientific Models - A New Way to Teach, Learn, and
Share Learning Experience, Elrefaei Hatem, Aboelfadel Tamer, Elmeseery Maha,
Elmofty Ali, Shafee Marwa, in Proceedings of the International Conference of "Interactive computer aided learning" ICL2007, Villach, Austria.\textbf{\underbar{}}
  \item El Meseery, Maha, Fakhr El Din, Mahmoud., Mashali, Samia., Fayek, Magda.
 \& Darwish, Nevin., Sketch Recognition Using Particle Swarm Algorithms,  IEEE International Conference on Image Processing, November,  2009.
  \item El Meseery, Sketch Recognition and Understanding,  Master Thesis,
  Faculty of Engineering, Computer Engineering Department, Cairo University,
  November, 2009.
  \item El Meseery, Maha, Fakhr El Din, Mahmoud., Tarek abouldahab, Sketch
  Recognition using Enhanced Particle Swarm Optimization, ICGST International Journal on Artificial Intelligence and Machine Learning  2010, (Under Review).
\end{enumerate}
 \section*{Awards:}
  \begin{enumerate}
    \item \textbf{1999} \textit{Excellence Reward} Faculty of Engineering.
    (The reward is given to students who attained a result of 'Very Good' each year).
    \item \textbf{2000} \textit{Excellence Reward}
    \item \textbf{2001} \textit{Excellence Reward}
    \item \textbf{2002} \textit{Excellence Reward}
    \item \textbf{2003} \textit{Excellence Reward}
  \end{enumerate}
 \section*{Computer Skills:}
 \begin{enumerate}
\item Environments: Linux (openSuse) and Windows.
 \item Programming: Java, JSP, Sturts, AJAX, .Net,C/C++, C\#,  ASP.NET, ASP, ADO.Net, ADO, VC6,  XML  Visual Basic, Embedded C, Assembly, Pascal, VHDL, Prolog, Lisp, Matlab, latex.
 \item Database Tools: SQL server 2000, MySql, Oracle and developer 6i.
 \item Analysis and Modeling: UML, Hardware design.
\end{enumerate}

@@

 \begin{enumerate}
\item 2010-Present, Online Handwriting project; a project to implement an Online Arabic handwriting system.
 \item 2009-2010, Arabic Digit Recognition project; a project to implement an Arabic Digit Recognition system with high accuracy and speed.
\item 2007-2008, Schedulizier project, a project to schedule and manage information of training companies ( Engnet Co.).
 \item 2006-2007, Scientific SDK, a project to help engineers create scientific simulations by automatically generating the user interfaces code for them.
 \item 2005-2006, Imodelit library scientific Microwave java applet library ( http:\textbackslash \textbackslash www.imodelit.com. Engnet Co.).
 \item 2004, Mouth detection and segmentation, using C++ (Pre Master Project).
 \item 2004, Traffic Control System using micro-controllers (Pre Master
 Project).
 \item 2003, Using Neural Network to recognize English Characters, using Matlab.
 \item 2003, Keyless Entry System has keypad to enter a password, display to display messages to the user automatic lock and unlock, using assembly of 80468.
 \item 2003, Implementing a Processor, using VHDL.
 \item 2002, Simulation of a single processor operating system, using Java.
 \item 2001, Developing a Database for a social security accounting office, using Oracle Database.
 \item 2001, Water Filter using sensors.
 \item 2000, Implementing a snake Game, using Pascal.
\end{enumerate}

@@

\begin{enumerate}
\item  Student member of the Institute of Electrical and Electronics Engineers
(IEEE) since 2002.
\item  Member of the Egyptian Engineering Syndicate (ESE) since 2003.
\item  Member of \textit{Resala} Charitable Society since 1999, responsible for
the following activities:
\begin{enumerate}
\item  Carrying out the big sister role for orphan girls. This includes the following
  \begin{enumerate}
\item Helping developing better education for \textit{Resala} organization
orphans.
\item Acting as guidance for behavioural, social and mental aspect of orphaned
teenagers.
\item Attend behaviour modification, social interaction with teenagers.
\item Give teenagers educational lessons to improve their quality of educations.
\end{enumerate}
\item  Organizing blood donations campaigns.
\item  Delivering free-charge courses in IT (C, C++, VC6, Windows and office ).
\item  Helping in writing the contents of tutorial for the various courses given at Resala ITcenter.
\end{enumerate}
\item  Member of El-Hosry Charitable Society since 2003.
\item  Member of Egyptian Army clubs.
\item  Member of shooting club, Dokki.
\item  Enjoy reading, swimming, walking and watching movies.
\end{enumerate}

\section*{References}
\noindent
\textbf{Dr. Magda Fayek}
 Address: Computer Engineering Dept., Faculty of Engineering, Cairo University, Giza, Egypt.
\\ \textbf{Email: }magdafayek@eng.cu.edu.eg.

\textbf{Dr. Hatem El refaei}
 Address: Physics and Mathematics Dept., Faculty of Engineering, Ain Shams University, Cairo, Egypt.
 \\ \textbf{Email: }hatem@mcit.gov.eg.

\textbf{Dr. Sherif Abdel Azeem}
 Address: Electrical Engineering Dept., School of Science and Engineering,
 American University in Cairo, New Cairo, Cairo, Egypt.\\ \textbf{Email: }
 shazeem@aucegypt.edu.

 \textbf{Dr Mahmoud Fakhr El Deen}
 Address: Computer and Systems Dept., Electronic Research Institute,
 National Research Center, Tahreer Street, Dokki, Cairo, Egypt.\\ \textbf{Email:
 } mafakhr@mcit.gov.eg.

\end{document}

>>>>

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{-0.25in}
\setlength\textheight{9.8in}
\setlength\textwidth{6.5in}
\setlength\oddsidemargin{-0.25in}
\setlength\evensidemargin{-0.25in}
\setlength\parindent{0in}
\setlength\parskip{0in}

@@

%%% remove comment delimiter ('%') and select language if required
%\selectlanguage{spanish}
\maketitle

 \section*{Education:}
  \begin{description}
 \item [2004-2009]  \textbf{ Msc.E., Cairo University, Computer Engineering Department, Giza, Egypt}\\
 Thesis Area:\textbf{\textit{Sketch Recognition And Understanding}.}\\
 Thesis Supervisors: \textit{Prof. Nevin Darwish (Cairo University), Dr Magda
 Fayek (Cairo University), Prof. Samia Mashali (Electrical Research Institute),
 Mahmoud Fakr El Din (Electrical Research Institute).}
 \item[1998-2003]  \textbf{ Bsc.E., Cairo University, Computer Engineering Department Giza, Egypt}\\
  Final Grade: \textbf{Very Good with honors.}\\
  Graduation project: \textit{Personal Face identification System,} \textbf{Distinction.}\\
  Project Supervisors: \textit{Dr. Madga Fayek.}

  \end{description}

 \section*{Experience:}
 %\textbf{\underbar{Experience:}}
 \textbf{August 2008- present   [part time]}\\
 \textbf{Research and Teaching Assistant}, American University in Cairo, Egypt,
 Electrical Engineering Department.

 \begin{enumerate}
   \item Conducting and helping develop research in Online Arabic Handwriting
   Recognition. This includes implementing various features extraction and classification methods.
   \item Assisting in collecting, gathering and analyzing an Online Arabic
   handwriting Dataset.
%   \item Assisting and developed research in area of Arabic and Latin digit
   Recognition.
 \item Implementing different features extraction and classification methods for Arabic and Latin digits and comparing their performance.
 \item Reading, analyzing and reviewing scientific and research papers.
 \item Guiding students in their studies in Lab projects and programming
 assignments.
 \item Conducting tutorials and problem sessions for students in various
 subjects.
\end{enumerate}

 \textbf{January 2007- present}\\
 \textbf{Research Assistant}, Electrical Research Institute, Egypt
 \begin{enumerate}
\item Working as a member of the Signal Processing Lab in the Computer and
Systems Department.
 \item Assisting in the research project undergoing in the department.
 \item Implementing and developing different algorithms in field of Image
 Processing.
 \item Providing a technical support for other researchers especially in field
 of JavaEE programming.
\end{enumerate}

 \textbf{September 2005- September 2008 [part time from January 2007] }\\
 \textbf{Senior Software Engineer}, EngNet, Egypt\textbf{}
 The following is summary of my achievements:
 \begin{enumerate}

@@

 \textbf{September 2003- September 2005}\\
 \textbf{Teaching Assistant}, Faculty of Computer Science, MSA University, Giza, Egypt.\textbf{}
 \begin{enumerate}
\item Developed lab manuals and leading lab experiments for Software Engineering
Methodologies, Object Oriented Programming, Digital Logic Design, Computer Graphics, Calculus, and Introduction to IT.
 \item Assistant supervisor for senior student's projects (Mainly graduation project using ASP.Net, C\#) .
 \item Developing and delivering short courses in C++, C\#, UML, and ASP.NET.
\end{enumerate}

 \section*{Publications:}
 \begin{enumerate}
  \item Online Library of Scientific Models - A New Way to Teach, Learn, and
Share Learning Experience, Elrefaei Hatem, Aboelfadel Tamer, Elmeseery Maha,
Elmofty Ali, Shafee Marwa, in Proceedings of the International Conference of "Interactive computer aided learning" ICL2007, Villach, Austria.\textbf{\underbar{}}
  \item El Meseery, Maha, Fakhr El Din, Mahmoud., Mashali, Samia., Fayek, Magda.
 \& Darwish, Nevin., Sketch Recognition Using Particle Swarm Algorithms,  IEEE
 International Conference on Image Processing, Cairo, Egypt, November,  2009.
  \item El Meseery, Sketch Recognition and Understanding,  Master Thesis,
  Faculty of Engineering, Computer Engineering Department, Cairo
  University, Egypt, November, 2009.
  \item El Meseery, Maha, Fakhr El Din, Mahmoud, Tarek abouldahab, Sketch
  Recognition using Enhanced Particle Swarm Optimization, (Submitted to)Pattern
  Recognition Letters, 2010, (17 pages).
\end{enumerate}
 \section*{Awards:}
  \begin{enumerate}
    \item \textbf{1999-2003} \textit{Excellence Reward} Faculty of Engineering,
    Cairo, Egypt.

  \end{enumerate}
 \section*{Computer Skills:}
 \begin{enumerate}
\item Environments: Linux (openSuse) and Windows.
 \item Programming: Java, JSP, Sturts, AJAX, .Net,C/C++, C\#,  ASP.NET, ASP, ADO.Net, ADO, VC6,  XML  Visual Basic, Embedded C, Assembly, Pascal, VHDL, Prolog, Lisp, Matlab, latex.
 \item Database Tools: SQL server 2000, MySql, Oracle and developer 6i.
 \item Analysis and Modeling: UML, Hardware design.
\end{enumerate}

@@

 \begin{enumerate}
\item 2010-Present, Online Handwriting project.
 \item 2009-2010, Arabic Digit Recognition project.
\item 2007-2008, Schedulizier: a project to schedule and manage information of
training companies ( EngNet, Egypt.).
 \item 2006-2007, Scientific SDK: a project to help engineers create scientific
 simulations by automatically generating the user interface for them.( EngNet,
 Egypt)
 \item 2005-2006, Imodelit : a library of scientific Microwave java applets (
 EngNet, Egypt).
 \item 2004, Mouth detection and segmentation using C++ (Master's Project).
 \item 2004, Traffic Control System using micro-controllers (Master's
 Project).
 \item 2003, Using Neural Network to recognize English Characters using Matlab.
 \item 2003, Keyless Entry System using 80468 assembly.
 \item 2003, Implementing a Processor using VHDL.
 \item 2002, Simulation of a single processor operating system using Java.
 \item 2001, Developing a Database for a social security accounting office using Oracle Database.
 \item 2001, Water Filter (Hardware project).
 \item 2000, Snake Game using Pascal.
\end{enumerate}

@@

\begin{enumerate}
\item  Student member of the Institute of Electrical and Electronics Engineers
(IEEE) since 2002.
\item  Member of the Egyptian Engineering Syndicate (ESE) since 2003.
\item  Member of \textit{Resala} Charitable Society since 1999, responsible for
the following activities:
\begin{enumerate}
\item  Carrying out the big sister role for orphan girls. This includes the following
  \begin{enumerate}
\item Helping developing better education procedures for \textit{Resala}
organization orphans.
\item Attend courses on behaviour modification and  social interaction for
teenagers.
\item Acting as guidance for behavioural, social and mental aspect for orphaned
teenagers.

\item Teach teenagers educational courses in different subjects.
\end{enumerate}
\item  Organizing blood donations campaigns.
\item  Delivering free-charge courses in IT (C, C++, VC6, Windows and office ).
\item  Helping in writing the contents of tutorial for the various courses given at Resala ITcenter.
\end{enumerate}
\item  Member of Egyptian shooting clubs.
\item  Enjoy reading, swimming, walking and watching movies.
\end{enumerate}
\newpage
\section*{Personal Information:}
\noindent
 \textbf{ Address: } $2^{nd}$ Tahreer street, Dokki, Giza 12615, Egypt.

\textbf{  Email: }  melmeseery@aucegypt.edu

\section*{References:}
%\noindent
\begin{description}

\item[\textbf{Dr. Magda Fayek}] (Professor)

\begin{description}
  \item[Address:]Computer Engineering Dept., Faculty of Engineering, Cairo University, Giza, Egypt.
  \item[Email:] magdafayek@eng.cu.edu.eg.
%\\\textbf{Email: }
\end{description}
\item[\textbf{Dr. Hatem El refaei}] (Associate Professor)

\begin{description}
  \item[Address:]Physics and Mathematics Dept., Faculty of Engineering, Ain Shams University, Cairo, Egypt.
  \item[Email:]hatem@mcit.gov.eg.
\end{description}

\item[\textbf{Dr. Sherif Abdel Azeem}] (Associate Professor)

\begin{description}
  \item[Address:]Electrical Engineering Dept., School of Science and Engineering,American University in Cairo, New Cairo, Cairo, Egypt.
  \item[Email:]  shazeem@aucegypt.edu.
\end{description}

\item[ \textbf{Dr. Mahmoud Fakhr El Deen}] (Researcher)

 \begin{description}
  \item[Address:]Computer and Systems Dept., Electronic Research Institute,
  National Research Center, Tahreer Street, Dokki, Cairo, Egypt.
  \item[Email:]mafakhr@mcit.gov.eg.
\end{description}
\end{description}
\end{document}
